Evolutionary rescue by aneuploidy in tumors exposed to anti-cancer drugs

### 2025-02-03 ResponseLetter.tex

Results:
* Figure 7 - Add a numerical solution to equation (D3)? This should make it clearer that the non-monotonicity of the black curve is an artefact of the simplifying assumptions in (D4) and not a problem with the approach.

\textcolor{blue}{We have added the green line for eq. D3 to Figure 7 as suggested. It is very close to the blue line for eq. D4.}

* By the way, It wasn't clear to me what happened to the other large $\tau_a^r$ terms in the first portion of equation (D3) when approximating the equation into the form shown in (D4)? Could this be briefly clarified?

\textcolor{blue}{
We have thoroughly revised Appendix D and the corresponding Figure S7 to make the derivations clearer.
}
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Appendix C: all dummy variable used in integration are consistent. %change r4

Figure S6, S7, S8, S9: changed the subscripts of several variables from $w$ to $s$ . %change r5

``If a fraction $f$ of the cancer cells are aneuploid when the drug is administered then the rates at which the rescue mutations are generated can be written as'' $\rightarrow$
``If a fraction $f$ of the cancer cells are aneuploid when the drug is administered then the expected number of successful mutants generated until time $t$ is given by''. % change r6

Revised the captions of supporting Figures S6-S9 to make them shorter and clearer.

### 2025-02-04 ms.tex
Add files via upload
Fixed Figure S6

Solid lines show our approximations (\cref{eq:AsymptoticTimeRules}) compared to red markers that show mean of simulations results (with error bars for 95\% confidence intervalues obtained with bootstrap, see Appendix G).

@@

Solid lines show our approximations (green: \cref{eq:t2det2} for $N>N_m^*$, blue:  \cref{meanproliferationtime2} with $\tau_a$ from \cref{eq:AsymptoticTimeRules} for $N<N_a^*$; black: \cref{meanproliferationtime2}) compared to red markers that show mean of simulations results (with error bars for 95\% confidence intervals obtained with bootstrap, see Appendix G).

>>>>

Solid lines show our approximations (green: \cref{limitapprox3}, blue: \cref{limitapprox4}, black: \cref{meantimet2}) compared to red markers that show mean of simulations results (with error bars for 95\% confidence intervalues obtained with bootstrap, see Appendix G).

@@

Solid lines show our approximations (green: \cref{eq:t2det2} for $N>N_m^*$, blue:  \cref{meanproliferationtime2} with $\tau_a$ from \cref{eq:AsymptoticTimeRules} for $N<N_a^*$; black: \cref{meanproliferationtime2} with $\tau_a$ from \cref{meantimet2}) compared to red markers that show mean of simulations results (with error bars for 95\% confidence intervals obtained with bootstrap, see Appendix G).
